Turned on!": Momentum in Round-Based First Person Shooter Esports

### 2022-07-19 presentation.qmd
update val dates

::: fragment
-   Plant/Defuse in Valorant
-   Valorant professional league, updated through January 1, 2022
-   5v5
-   First to 13 round wins
-   One team plays offense in 12 consecutive rounds before swapping sides
-   Must win by 2 cod_rounds
:::

@@

# Joshua Broas, vlr.gg
common_val_labs <- function(...) {
  list(
    ...,
    labs(
      caption = 'Pro Valorant matches, 2020 - Jan 1, 2022'
    )
  )
}

>>>>

::: fragment
-   Plant/Defuse in Valorant
-   Valorant Champions Tour (VCT) matches (qualifiers and majors), through November 11, 2021
-   5v5
-   First to 13 round wins
-   One team plays offense in 12 consecutive rounds before swapping sides
-   Must win by 2 cod_rounds
:::

@@

# Joshua Broas, vlr.gg
common_val_labs <- function(...) {
  list(
    ...,
    labs(
      caption = '2021 VCT matches'
    )
  )
}
